A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2014-03-13 paper/draft.tex
Added announce for the article structure

@@

To sum up,  the adoption of MH could  increase feature set introduced by nested virtualization adoption. The first impeding problem is the implementation of MH, able to propose to guest to virtualize with hardware assistance. In next section, we present an implementation of GPH over MH, that try to circumvent this limitation leveraging paravirtualization.

\section{Implementation}
In the previous sections we proposed a functional analysis of cloud architecture in order to respect design principles that we identified in the introduction. In this section, we propose a GPH over MH implementation, based on Xen over NOVA.

>>>>

The reste of the paper in organized as follows. In Section 2 we start analyzing related work. In section 3, we analyze current limitations of classical nested virtualization approach and in section 4 we analyze the microvisor approach. In section 5 we analyzes cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before. Furthermore, in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section  in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

@@

To sum up,  the adoption of MH could  increase feature set introduced by nested virtualization adoption. The first impeding problem is the implementation of MH, able to propose to guest to virtualize with hardware assistance. In next section, we present an implementation of GPH over MH, that try to circumvent this limitation leveraging paravirtualization.
 \section{Implementation}
In the previous sections we proposed a functional analysis of cloud architecture in order to respect design principles that we identified in the introduction. In this section, we propose a GPH over MH implementation, based on Xen over NOVA.
